---
title: "R Notebook VPD crime"
output: html_notebook
---



```{r}
crime <- read.csv("crime-in-vancouver/crime.csv")

```

```{r}
summary(crime)
```
```{r}
length(unique(crime$HUNDRED_BLOCK))
length(unique(crime$NEIGHBOURHOOD))
```
#tidy time replace hour and min with Mean
```{r}
crime$HOUR
crime$HOUR [is.na(crime$HOUR)]<-15.00
crime$MINUTE[is.na(crime$MINUTE)]<-17.00
head(crime)
crime$MINUTE
```
# use Neighbourhood
# top 10 blocks high crime type
# crime per hood


#year vs Crime count histgram
```{r}
#year vs Crime count histgram
ggplot(crime, aes(x = YEAR))+
  geom_histogram(binwidth = 0.5)

#month vs Crime count histgram
ggplot(crime, aes(x = MONTH))+
  geom_histogram(binwidth = 0.5)
```


#NEIGHBOURHOOD vs Crime
```{R}
ggplot(crime, aes(x = NEIGHBOURHOOD))+
  geom_bar()+
  theme(axis.text.x=element_text(size=7, 
                                     angle = 90,
                                     ))
```



```{r}
summary(crime$NEIGHBOURHOOD)
head (crime$NEIGHBOURHOOD)
```

```{r}

```

```{R}
crime$NEIGHBOURHOOD[crime$NEIGHBOURHOOD== ""] <- NA
ggplot(crime, aes(x = NEIGHBOURHOOD),na.rm = TRUE)+
  geom_bar()+
  theme(axis.text.x=element_text(size=8, 
                                     angle = 90
                                    ))

```

```{r}
summary(crime$NEIGHBOURHOOD)
```


#Neighbourhood vs crime count by type of crime 
```{R}
ggplot(crime, aes(x = NEIGHBOURHOOD, fill = factor(TYPE)))+
  geom_bar(position  = "fill")+
  theme(axis.text.x=element_text(size=8, 
                                     angle = 90
                                    ))
#new.crime1 excludes break and enter/Vehicle collision
ggplot(new.crime1, aes(x = NEIGHBOURHOOD, fill = factor(TYPE)))+ 
  geom_bar(position  = "fill")+
  theme(axis.text.x=element_text(size=8, 
                                     angle = 90
                                    ))
```

```{r}
length(unique(crime$TYPE))
summary(crime$TYPE)
```

# Creat data without Vehicle Collision, Break and Enter

```{r}
head(crime$TYPE)
```


```{r}

new.crime <- crime[!grepl('Pedestrian', crime$TYPE),] #without pedestrian
new.crime1 <- new.crime [!grepl('Break', new.crime$TYPE),] # without Break and enter

```

```{r}
summary(new.crime1)
```

# color for heat map
#data set for year, type, sum

heat <- new.crime1 (TYPE,YEAR,)

library("RColorBrewer")
myColors <- brewer.pal(9, "Blues")

ggplot(new.crime1, aes(x= YEAR, y= TYPE,  ))+
  geom_tile()+
  facet_wrap( ~ NEIGHBOURHOOD , ncol = 1)
  
```{r}
vehicle.df <- new.crime1 [new.crime1 == "Theft of Vehicle",]
head(vehicle.df)
```

```{r}
which (is.na(vehicle.df$NEIGHBOURHOOD))
```

```{r}
vehicle.df[!grepl('NA', vehicle.df$NEIGHBOURHOOD),] #no NA
str(vehicle.df)
summary(vehicle.df)
```

```{r}
vehicle1.df <- vehicle.df[!grepl('NA', vehicle.df$NEIGHBOURHOOD),] #no NA

```

```{r}
vehicle.df$NEIGHBOURHOOD

```




```{r}
which (is.na(vehicle.df$NEIGHBOURHOOD))
```
nona.vehicle <- vehicle.df[!grepl("NA", vehicle.df$NEIGHBOURHOOD),]



```{r}
ggplot(vehicle1.df, aes(x = NEIGHBOURHOOD))+
  geom_bar()+
  theme(axis.text.x=element_text(size=7, 
                                     angle = 90,
                                     ))
```


